Active Learning for SAT Solver Benchmarking

### 2022-10-08 paper/paper.tex
Revise Abstract
Only language. Also, get rid off the last line only containing one word.

\begin{abstract}
  Benchmarking is one of the most important phases in the development of algorithms.
  This also applies to solutions of the SAT problem (propositional sat\-is\-fia\-bi\-li\-ty).
  While the field of SAT solver benchmarking is well established, traditional benchmark selection approaches do not optimize for benchmark runtime.
  Benchmark compilation selects representative instances from a pool of instances such that they reliably discriminate SAT solvers based on their runtime.
  In this paper, we present an active learning based dynamic benchmark selection approach that predicts the rank of a new solver among its competitors with minimum running time and maximum rank prediction accuracy.
  We evaluated this approach using the Anniversary track dataset from the 2022 SAT Competition. 
  Our dynamic instance selection approach can predict the rank of a new solver after about \SI{10}{\%} of the time it would take to run the solver on all instances of this dataset, with a prediction accuracy of about \SI{92}{\%}. 
  In this paper, we also discuss the importance of instance families in the selection process. 
  Our tool provides a reliable way for SAT solver engineers to efficiently determine the performance of a new SAT solver.

>>>>

\begin{abstract}
  Benchmarking is one of the most important phases when developing algorithms.
  This also applies to solutions of the SAT (propositional satisfiability) problem.
  While the field of SAT solver benchmarking is well established, traditional benchmark selection approaches do not optimize for benchmark runtime.
  Benchmark selection chooses representative instances from a pool of instances such that they reliably discriminate SAT solvers based on their runtime.
  In this paper, we present a dynamic benchmark selection approach based on active learning.
  Our approach predicts the rank of a new solver among its competitors with minimum running time and maximum rank prediction accuracy.
  We evaluated this approach using the Anniversary Track dataset from the 2022 SAT Competition.
  Our selection approach can predict the rank of a new solver after about \SI{10}{\%} of the time it would take to run the solver on all instances of this dataset, with a prediction accuracy of about \SI{92}{\%}. 
  In this paper, we also discuss the importance of instance families in the selection process. 
  Overall, our tool provides a reliable way for SAT solver engineers to efficiently determine the performance of a new SAT solver.
